### 2017-04-06 paper/evaluation.tex
partial changes

To understand why developers prefer not use parallel test execution,
we considered \numNonParallel{} subjects that do not use parallel
configuration as default test execution from Section~\ref{sec:rqC-1} and elaborated a
quick survey to extent the comprehension about why developers do not
use parallel configuration. \Luis{describe how we created the survey}.
We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the 
\numNonParallel{} projects, and we did not found any e-mail from
\Fix{??} projects using \CodeIn{git} tool.
\Luis{Here I want to say that I could not found any valid e-mail using
\textit{git log}}
There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
projects, and \emailsFalseAnswers{} developers was not able to 
explain how the testing works or was not able to answer the survey.

>>>>

To answer this research question we surveyed developers involved in a
selection of projects listed in Section~\ref{sec:rqC-1}.  The goal of
the survey is to better comprehend developer's attitude towards use of
parallelism to speedup regression testing in open-source projects.

we considered \numNonParallel{} subjects that do not use parallel
configuration as default test execution from

We first retrieve the last 20 commits from the project repository and
got the developers e-mails. In total, we sent an e-mail to
\emailsSent{} developers that recently contributed to the 
\numNonParallel{} projects, and we did not found any e-mail from
\Fix{??} projects using \CodeIn{git} tool.
\Luis{Here I want to say that I could not found any valid e-mail using
\textit{git log}}
There were \emailsAnswered{} replies from \emailsProjectsAnswered{}
projects, and \emailsFalseAnswers{} developers was not able to 
explain how the testing works or was not able to answer the survey.
